Equations & R Code

### 2017-03-22 manuscript/coexistence-stability_SI.Rmd
updates results text with sensitivity analysis

  ####
  #### Simulate model -----------------------------------------------------
  ####
  days           <- c(1:days_to_track)
  num_spp        <- length(parms$r)
  nmsDNR         <- names(DNR)
  dormants       <- grep("D", names(DNR))
  NR             <- DNR[-dormants] 
  nmsNR          <- names(NR)
  gVec           <- getG(sigE = sigE, rho = rho, nTime = seasons, num_spp = num_spp)
  Rvector        <- urlnorm(seasons, Rmu, Rsd_annual, lb = 0, ub = 200)
  saved_outs     <- matrix(ncol=length(DNR), nrow=seasons+1)
  saved_outs[1,] <- DNR

>>>>

  ####
  #### Simulate model -----------------------------------------------------
  ####
  days           <- c(1:days_to_track)
  num_spp        <- length(parms$r)
  nmsDNR         <- names(DNR)
  dormants       <- grep("D", names(DNR))
  NR             <- DNR[-dormants] 
  nmsNR          <- names(NR)
  gVec           <- getG(sigE = sigE, rho = rho, nTime = seasons, num_spp = num_spp)

  if(Rsd_annual == 0) {
    Rvector        <- rlnorm(seasons, Rmu, Rsd_annual)
  }
  if(Rsd_annual > 0) {
    Rvector        <- urlnorm(seasons, Rmu, Rsd_annual, lb = 0, ub = 200)
  }

  saved_outs     <- matrix(ncol=length(DNR), nrow=seasons+1)
  saved_outs[1,] <- DNR

### 2017-03-22 manuscript/coexistence-stability_SI.tex
updates results text with sensitivity analysis

  \NormalTok{####}
  \NormalTok{#### Simulate model -----------------------------------------------------}
  \NormalTok{####}
  \NormalTok{days           <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{:days_to_track)}
  \NormalTok{num_spp        <-}\StringTok{ }\KeywordTok{length}\NormalTok{(parms$r)}
  \NormalTok{nmsDNR         <-}\StringTok{ }\KeywordTok{names}\NormalTok{(DNR)}
  \NormalTok{dormants       <-}\StringTok{ }\KeywordTok{grep}\NormalTok{(}\StringTok{"D"}\NormalTok{, }\KeywordTok{names}\NormalTok{(DNR))}
  \NormalTok{NR             <-}\StringTok{ }\NormalTok{DNR[-dormants] }
  \NormalTok{nmsNR          <-}\StringTok{ }\KeywordTok{names}\NormalTok{(NR)}
  \NormalTok{gVec           <-}\StringTok{ }\KeywordTok{getG}\NormalTok{(}\DataTypeTok{sigE =} \NormalTok{sigE, }\DataTypeTok{rho =} \NormalTok{rho, }\DataTypeTok{nTime =} \NormalTok{seasons, }\DataTypeTok{num_spp =} \NormalTok{num_spp)}
  \NormalTok{Rvector        <-}\StringTok{ }\KeywordTok{urlnorm}\NormalTok{(seasons, Rmu, Rsd_annual, }\DataTypeTok{lb =} \DecValTok{0}\NormalTok{, }\DataTypeTok{ub =} \DecValTok{100}\NormalTok{)}
  \NormalTok{saved_outs     <-}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\DataTypeTok{ncol=}\KeywordTok{length}\NormalTok{(DNR), }\DataTypeTok{nrow=}\NormalTok{seasons}\DecValTok{+1}\NormalTok{)}
  \NormalTok{saved_outs[}\DecValTok{1}\NormalTok{,] <-}\StringTok{ }\NormalTok{DNR }

>>>>

  \NormalTok{####}
  \NormalTok{#### Simulate model -----------------------------------------------------}
  \NormalTok{####}
  \NormalTok{days           <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{:days_to_track)}
  \NormalTok{num_spp        <-}\StringTok{ }\KeywordTok{length}\NormalTok{(parms$r)}
  \NormalTok{nmsDNR         <-}\StringTok{ }\KeywordTok{names}\NormalTok{(DNR)}
  \NormalTok{dormants       <-}\StringTok{ }\KeywordTok{grep}\NormalTok{(}\StringTok{"D"}\NormalTok{, }\KeywordTok{names}\NormalTok{(DNR))}
  \NormalTok{NR             <-}\StringTok{ }\NormalTok{DNR[-dormants] }
  \NormalTok{nmsNR          <-}\StringTok{ }\KeywordTok{names}\NormalTok{(NR)}
  \NormalTok{gVec           <-}\StringTok{ }\KeywordTok{getG}\NormalTok{(}\DataTypeTok{sigE =} \NormalTok{sigE, }\DataTypeTok{rho =} \NormalTok{rho, }\DataTypeTok{nTime =} \NormalTok{seasons, }\DataTypeTok{num_spp =} \NormalTok{num_spp)}

  \NormalTok{if(Rsd_annual ==}\StringTok{ }\DecValTok{0}\NormalTok{) \{}
    \NormalTok{Rvector        <-}\StringTok{ }\KeywordTok{rlnorm}\NormalTok{(seasons, Rmu, Rsd_annual)}
  \NormalTok{\}}
  \NormalTok{if(Rsd_annual >}\StringTok{ }\DecValTok{0}\NormalTok{) \{}
    \NormalTok{Rvector        <-}\StringTok{ }\KeywordTok{urlnorm}\NormalTok{(seasons, Rmu, Rsd_annual, }\DataTypeTok{lb =} \DecValTok{0}\NormalTok{, }\DataTypeTok{ub =} \DecValTok{200}\NormalTok{)}
  \NormalTok{\}}

  \NormalTok{saved_outs     <-}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\DataTypeTok{ncol=}\KeywordTok{length}\NormalTok{(DNR), }\DataTypeTok{nrow=}\NormalTok{seasons}\DecValTok{+1}\NormalTok{)}
  \NormalTok{saved_outs[}\DecValTok{1}\NormalTok{,] <-}\StringTok{ }\NormalTok{DNR }

### 2017-03-22 manuscript/coexistence-stability_ms.Rmd
updates results text with sensitivity analysis

MATERIALS AND METHODS
---------------------
\new{To bound the problem and to isolate the effect of fluctation-dependent coexistence on the diversity--ecosystem variability relationship we constrain our analysis to four species communities and do not consider communities where coexistence is maintained by a combination of mechanisms.
We limit our analysis to four species communities to keep the models tractable while still allowing enough of a species richness gradient for trends to emerge.
It is exceedingly difficult to get more than four species to coexist via relative nonlinearity without introducing some form of fluctuation-independent mechanism like resource partitioning} [@Yuan2015], \new{which would then cloud our inference on the effect of fluctuation-dependent coexistence.
So, for consistency we also constrain our focus to four species communities under the storage effect, but our conclusions generally apply to more species-rich communities too (see SI section SI.2).}

@@

We assume the resource pool is not replenished within a growing season.
Resource replenishment occurs between growing seasons, and the resource pool (*R*) at the start of the growing season is $R_{\tau(0)} = R^+$, where $R^+$ is a random resource pulse drawn from a log-normal distribution with mean $\mu(R^+)$ and standard deviation $\sigma(R^+)$. 
\new{Taken all together, we can combine equations 1 and 4 to define the discrete transitions between live and dormant biomass at the end of a growing season.
Thus, the initial conditions for each state ($D, N, R$) at the beginning of growing season $\tau+1$ are:}
\vspace{-3em}
\begin{align}
  D_{i,\tau(0) + 1} &= (1-\gamma_{i,\tau}) \left[\alpha_i N_{i,\tau(T)} + D_{i,\tau(T)} \right] (1-\eta_i) \\
  N_{i,\tau(0) + 1} &= \gamma_{i,\tau} \left[\alpha_i N_{i,\tau(T)} + D_{i,\tau(T)} \right] (1-\eta_i) \\
  R_{\tau + 1} &= \text{lognormal}\left(\mu(R^+), \sigma(R^+) \right)_0^{200},
\end{align}
\vspace{-3em}
\noindent \new{where, as above, $\tau(T)$ denotes the end of growing season $\tau$ and $\tau(0) + 1$ denotes the beginning of growing season $\tau+1$.} 
\new{The subscript (0) and superscript (200) indicates a lognormal distribution truncated at those values.
We used the function \texttt{urlnorm} from the Runuran package (CITATION) to generate values from the truncated lognormal distribution.}
Model parameters and notation are described in Table 1.

@@

### Numerical simulations
To explore how fluctuation-dependent coexistence can affect the diversity--ecosystem variability relationship, we simulated the model with four species under two scenarios for each coexistence mechanism.
First, we allowed the variance of the environment to determine how many species can coexist, akin to a community assembly experiment with a species pool of four species.
\new{To do this, we simulated communities with all species initially present across a gradient of annual resource variability for relative nonlinearity (50 values of $\sigma_R$ in the range [0, 1.4]) or environmental cue variability for the storage effect (100 values of $\sigma_E^2$ in the range [0, 3]).}
Second, we chose parameter values that allowed coexistence of all four species and then performed species removals \new{at a single level of environmental variability}, akin to a biodiversity--ecosystem function experiment.
The two simulation experiments correspond to (i) sampling ecosystem function across a natural gradient of species richness and (ii) sampling ecosystem function across diversity treatments within a site.
\new{We refer to the former as a "regional" relationship, and the latter as a "local" relationship.
But note that we do not attribute any particular area size to "region", it is simply any area over which a gradient of environmental variability can emerge.}

To understand how increasing environmental variability will impact ecosystem variability when coexistence is fluctuation-dependent, we simulated the model over a range of species pool sizes and environmental cue or resource variability.
For each size of species pool (1, 2, 3, or 4 species), we simulated the model at 15 evenly-spaced levels of environmental cue (range = 0.1,2) for the storage effect and 25 evenly-spaced levels of resource variability (range = 0.1,1.4) for relative nonlinearity.
We also explored the influence of asymmetries in species' competitive abilities and correlations in species' environmental responses within the storage effect model.

@@

\new{For parameters that we did not vary, we chose values that would allow coexistence of all four species at some point along the environmental variability gradients we simulated.
Our focus is specifically on communities where fluctuation-dependent coexistence is operating, and making parameters increasingly asymmetric among species typically reduced coexistence strength or made coexistence impossible (Supporting Information section SI.2).
Changes in the absolute values of parameters also altered the strength of coexistence, but in no case did altering parameter values change the qualitative results and conclusions we present below (see Supporting Information section SI.2; Figs. SI-1,SI-2,SI-3).}
Parameter values for specific results are given in figure captions.

@@

\new{For the storage effect, total community \emph{CV} decreased with species richness at a given level of environmental variability because additional species reduced the temporal standard deviation due to portfolio effects (Fig. SI-7).
Mean biomass remained the same because all species had the same resource uptake functions, which was necessary to eliminate any potential effects of relative nonlinearity in growth.
For relative nonlinearity, total community \emph{CV} decreased with species richness at a given level of environmental variability because additional species increased mean biomass (over-yeilding) and, generally, reduced the temporal standard deviation (Fig. SI-7).
Mean biomass increased because some species had higher growth rates (Fig. SI-5), increasing total biomass.}

@@

@@

When we allowed communities to assemble at sites across a gradient of environmental variability, we discovered a positive relationship between species richness and ecosystem variability (Fig. 2A,C).
While surprising when viewed through the lens of biodiversity--ecosystem functioning theory and experimental findings, such a relationship is predicted by theory on coexistence in fluctuating environments.
Environmental variability is a prerequisite for the storage effect and relative nonlinearity to stabilize coexistence [@Chesson2000].
These mechanisms can translate increased variability into higher species richness (Fig. SI-2), but the increase in environmental variability also increases ecosystem variability.
\new{We limited our primary analysis to four-species communities, but the buffering effect of additional species under the storage effect is even stronger in more species rich communities (Fig. SI-x.}

>>>>

MATERIALS AND METHODS
---------------------
\new{To bound the problem and to isolate the effect of fluctation-dependent coexistence on the diversity--ecosystem variability relationship we constrain our analysis to four species communities and do not consider communities where coexistence is maintained by a combination of mechanisms.
We limit our analysis to four species communities to keep the models tractable while still allowing enough of a species richness gradient for trends to emerge.
It is exceedingly difficult to get more than four species to coexist via relative nonlinearity without introducing some form of fluctuation-independent mechanism like resource partitioning} [@Yuan2015], \new{which would then cloud our inference on the effect of fluctuation-dependent coexistence.
For consistency, we also constrain our focus to four species communities under the storage effect, but our conclusions generally apply to more species-rich communities, too (see Supporting Information section SI.2).}

@@

We assume the resource pool is not replenished within a growing season.
Resource replenishment occurs between growing seasons, and the resource pool (*R*) at the start of the growing season is $R_{\tau(0)} = R^+$, where $R^+$ is a random resource pulse drawn from a log-normal distribution with mean $\mu(R^+)$ and standard deviation $\sigma(R^+)$. 
\new{Taken all together, we can combine equations 1 and 4 to define the discrete transitions between live and dormant biomass at the end of a growing season.
Thus, the initial conditions for each state ($D, N, R$) at the beginning of growing season $\tau+1$ are:}
\vspace{-3em}
\begin{align}
  D_{i,\tau(0) + 1} &= (1-\gamma_{i,\tau}) \left[\alpha_i N_{i,\tau(T)} + D_{i,\tau(T)} \right] (1-\eta_i) \\
  N_{i,\tau(0) + 1} &= \gamma_{i,\tau} \left[\alpha_i N_{i,\tau(T)} + D_{i,\tau(T)} \right] (1-\eta_i) \\
  R_{\tau + 1} &= \text{lognormal}\left(\mu(R^+), \sigma(R^+) \right)_0^{200},
\end{align}
\vspace{-3em}
\noindent \new{where, as above, $\tau(T)$ denotes the end of growing season $\tau$ and $\tau(0) + 1$ denotes the beginning of growing season $\tau+1$.} 
\new{The subscript (0) and superscript (200) indicates a lognormal distribution truncated at those values.
We used the function \texttt{urlnorm} from the "Runuran" package} [@Leydold2015] \new{to generate values from the truncated lognormal distribution.}
Model parameters and notation are described in Table 1.

@@

### Numerical simulations
To explore how fluctuation-dependent coexistence can affect the diversity--ecosystem variability relationship, we simulated the model with four species under two scenarios for each coexistence mechanism.
First, we allowed the variance of the environment to determine how many species can coexist, akin to a community assembly experiment with a species pool of four species.
\new{To do this, we simulated communities with all species initially present across a gradient of annual resource variability for relative nonlinearity (50 evenly-spaced values of $\sigma_R$ in the range [0, 1.2]) or environmental cue variability for the storage effect (100 evenly-spaced values of $\sigma_E^2$ in the range [0, 3]).}
Second, we chose parameter values that allowed coexistence of all four species and then performed species removals \new{at a single level of environmental variability}, akin to a biodiversity--ecosystem function experiment.
The two simulation experiments correspond to (i) sampling ecosystem function across a natural gradient of species richness and (ii) sampling ecosystem function across diversity treatments within a site.
\new{We refer to the former as a "regional" relationship, and the latter as a "local" relationship.
But note that we do not attribute any particular area size to "region", it is simply any area over which a gradient of environmental variability can emerge.}

To understand how increasing environmental variability will impact ecosystem variability when coexistence is fluctuation-dependent, we simulated the model over a range of species pool sizes and environmental cue or resource variability.
For each size of species pool (1, 2, 3, or 4 species), we simulated the model at 15 evenly-spaced levels of environmental cue (range = [0.1, 2]) for the storage effect and 25 evenly-spaced levels of resource variability (range = [0, 1.2]) for relative nonlinearity.
We also explored the influence of asymmetries in species' competitive abilities and correlations in species' environmental responses within the storage effect model.

@@

\new{For parameters that we did not vary, we chose values that would allow coexistence of all four species at some point along the environmental variability gradients we simulated.
Our focus is specifically on communities where fluctuation-dependent coexistence is operating, and making parameters increasingly asymmetric among species typically reduced coexistence strength or made coexistence impossible (Supporting Information section SI.3).
Changes in the absolute values of parameters also altered the strength of coexistence, but in no case did altering parameter values change the qualitative results and conclusions we present below (see Supporting Information section SI.3).}
Parameter values for specific results are given in figure captions.

@@

\new{For the storage effect, total community \emph{CV} decreased with species richness at a given level of environmental variability because additional species reduced the temporal standard deviation due to portfolio effects (Fig. SI-7).
Mean biomass remained the same because all species had the same resource uptake functions, which was necessary to eliminate any potential effects of relative nonlinearity in growth.
Portfolio effects under the storage effect remained strong in an eight-species community, where total community \emph{CV} saturated after the fifth species (Fig. SI-x).
For relative nonlinearity, total community \emph{CV} decreased with species richness at a given level of environmental variability because additional species increased mean biomass (over-yeilding) and, at higher richness (three to four species), reduced the temporal standard deviation (Fig. SI-7).
Mean biomass increased because some species had higher growth rates (Fig. SI-5), increasing total biomass.}

@@

\new{We tested the qualitative generality of our results under different parameters by conducting a targeted sensitivity analysis focused on parameter values and asymmetries that most affect species coexistence (Supporting Information section SI.3).
Making parameters asymmetric induces competitive hierachies and makes coexistence more difficult.
For the storage effect, this is evident in Fig. 3 where we made live-to-dormant transition rates ($\alpha$s) asymmetric, and we achieved the same result when we made dormant mortality rates ($\eta$s) asymmetric (Fig. SI-x).
Furthermore, increasing the absolute value of dormant mortality also made coexistence more difficult, but results were qualitatively similar to those above.
For relative nonlinearity, altering the absolute value of the mean resource pulse shifts where species can coexist across a gradient of resource variability (Fig. SI-x).
But, again, qualitatively similar results emerge when species \emph{can} coexist.
In general, altering any parameter in isolation will make coexistence easier or harder at any given level of environmental variability.
Thus, our results are robust in the sense that the qualitative patterns we present will always emerge when the particular parameter values permit species coexistence over some range of envrionmental variability.
In other words, our results are only sensitive to whether fluctuation-dependent coexistence is operating, or not.}

@@

When we allowed communities to assemble at sites across a gradient of environmental variability, we discovered a positive relationship between species richness and ecosystem variability (Fig. 2A,C).
While surprising when viewed through the lens of biodiversity--ecosystem functioning theory and experimental findings, such a relationship is predicted by theory on coexistence in fluctuating environments.
Environmental variability is a prerequisite for the storage effect and relative nonlinearity to stabilize coexistence [@Chesson2000].
These mechanisms can translate increased variability into higher species richness (Fig. SI-2), but the increase in environmental variability also increases ecosystem variability.
\new{We limited our primary analysis to four-species communities, but the buffering effect of additional species under the storage effect is even stronger in more species rich communities (Fig. SI-x).}

### 2017-03-22 manuscript/coexistence-stability_ms.tex
updates results text with sensitivity analysis

\noindent \new{where, as above, $\tau(T)$ denotes the end of growing season $\tau$ and $\tau(0) + 1$ denotes the beginning of growing season $\tau+1$.}
\new{The subscript (0) and superscript (200) indicates a lognormal distribution truncated at those values.
We used the function \texttt{urlnorm} from the Runuran package (CITATION) to generate values from the truncated lognormal distribution.}
Model parameters and notation are described in Table 1.

@@

To explore how fluctuation-dependent coexistence can affect the
diversity--ecosystem variability relationship, we simulated the model
with four species under two scenarios for each coexistence mechanism.
First, we allowed the variance of the environment to determine how many
species can coexist, akin to a community assembly experiment with a
species pool of four species.
\new{To do this, we simulated communities with all species initially present across a gradient of annual resource variability for relative nonlinearity (50 values of $\sigma_R$ in the range [0, 1.4]) or environmental cue variability for the storage effect (100 values of $\sigma_E^2$ in the range [0, 3]).}
Second, we chose parameter values that allowed coexistence of all four
species and then performed species removals
\new{at a single level of environmental variability}, akin to a
biodiversity--ecosystem function experiment. The two simulation
experiments correspond to (i) sampling ecosystem function across a
natural gradient of species richness and (ii) sampling ecosystem
function across diversity treatments within a site.
\new{We refer to the former as a "regional" relationship, and the latter as a "local" relationship.
But note that we do not attribute any particular area size to "region", it is simply any area over which a gradient of environmental variability can emerge.}

To understand how increasing environmental variability will impact
ecosystem variability when coexistence is fluctuation-dependent, we
simulated the model over a range of species pool sizes and environmental
cue or resource variability. For each size of species pool (1, 2, 3, or
4 species), we simulated the model at 15 evenly-spaced levels of
environmental cue (range = 0.1,2) for the storage effect and 25
evenly-spaced levels of resource variability (range = 0.1,1.4) for
relative nonlinearity. We also explored the influence of asymmetries in
species' competitive abilities and correlations in species'
environmental responses within the storage effect model.

@@

When we allowed communities to assemble at sites across a gradient of
environmental variability, we discovered a positive relationship between
species richness and ecosystem variability (Fig. 2A,C). While surprising
when viewed through the lens of biodiversity--ecosystem functioning
theory and experimental findings, such a relationship is predicted by
theory on coexistence in fluctuating environments. Environmental
variability is a prerequisite for the storage effect and relative
nonlinearity to stabilize coexistence (Chesson 2000a). These mechanisms
can translate increased variability into higher species richness (Fig.
SI-2), but the increase in environmental variability also increases
ecosystem variability.
\new{We limited our primary analysis to four-species communities, but the buffering effect of additional species under the storage effect is even stronger in more species rich communities (Fig. SI-x.}

@@

\hypertarget{ref-DeClerck2006}{}
DeClerck, F.A.J., Barbour, M.G. \& Sawyer, J.O. (2006). SPECIES RICHNESS
AND STAND STABILITY IN CONIFER FORESTS OF THE SIERRA NEVADA.
\emph{Ecology}, 87, 2787--2799.

@@

>>>>

\noindent \new{where, as above, $\tau(T)$ denotes the end of growing season $\tau$ and $\tau(0) + 1$ denotes the beginning of growing season $\tau+1$.}
\new{The subscript (0) and superscript (200) indicates a lognormal distribution truncated at those values.
We used the function \texttt{urlnorm} from the "Runuran" package}
(Leydold \& Hörmann 2015)
\new{to generate values from the truncated lognormal distribution.}
Model parameters and notation are described in Table 1.

@@

To explore how fluctuation-dependent coexistence can affect the
diversity--ecosystem variability relationship, we simulated the model
with four species under two scenarios for each coexistence mechanism.
First, we allowed the variance of the environment to determine how many
species can coexist, akin to a community assembly experiment with a
species pool of four species.
\new{To do this, we simulated communities with all species initially present across a gradient of annual resource variability for relative nonlinearity (50 evenly-spaced values of $\sigma_R$ in the range [0, 1.2]) or environmental cue variability for the storage effect (100 evenly-spaced values of $\sigma_E^2$ in the range [0, 3]).}
Second, we chose parameter values that allowed coexistence of all four
species and then performed species removals
\new{at a single level of environmental variability}, akin to a
biodiversity--ecosystem function experiment. The two simulation
experiments correspond to (i) sampling ecosystem function across a
natural gradient of species richness and (ii) sampling ecosystem
function across diversity treatments within a site.
\new{We refer to the former as a "regional" relationship, and the latter as a "local" relationship.
But note that we do not attribute any particular area size to "region", it is simply any area over which a gradient of environmental variability can emerge.}

To understand how increasing environmental variability will impact
ecosystem variability when coexistence is fluctuation-dependent, we
simulated the model over a range of species pool sizes and environmental
cue or resource variability. For each size of species pool (1, 2, 3, or
4 species), we simulated the model at 15 evenly-spaced levels of
environmental cue (range = {[}0.1, 2{]}) for the storage effect and 25
evenly-spaced levels of resource variability (range = {[}0, 1.2{]}) for
relative nonlinearity. We also explored the influence of asymmetries in
species' competitive abilities and correlations in species'
environmental responses within the storage effect model.

@@

When we allowed communities to assemble at sites across a gradient of
environmental variability, we discovered a positive relationship between
species richness and ecosystem variability (Fig. 2A,C). While surprising
when viewed through the lens of biodiversity--ecosystem functioning
theory and experimental findings, such a relationship is predicted by
theory on coexistence in fluctuating environments. Environmental
variability is a prerequisite for the storage effect and relative
nonlinearity to stabilize coexistence (Chesson 2000a). These mechanisms
can translate increased variability into higher species richness (Fig.
SI-2), but the increase in environmental variability also increases
ecosystem variability.
\new{We limited our primary analysis to four-species communities, but the buffering effect of additional species under the storage effect is even stronger in more species rich communities (Fig. SI-x).}

@@

\hypertarget{ref-DeClerck2006}{}
DeClerck, F.A.J., Barbour, M.G. \& Sawyer, J.O. (2006). Species richness
and stand stability in conifer forests of the Sierra Nevada.
\emph{Ecology}, 87, 2787--2799.

@@

\hypertarget{ref-Leydold2015}{}
Leydold, J. \& Hörmann, W. (2015). Runuran: R Interface to the UNU.RAN
Random Variate Generators.
